Proposal full title \\ Proposal Acronym

### 2001-10-10 drafts/IST/PartC.tex
english and formatting fixes
svn path=/trunk/; revision=1526

\chapter*{C4. Contribution to Community social objectives}
\addcontentsline{toc}{chapter}{C4. Contribution to Community social objectives}
\
\textit{This section, not exceeding two pages, should describe how the proposed
subject wil contribute to meeting the social objectives of the Community, and
should focus on the contribution of the project to improving employment
prospects and the use and development of skills in Europe. \\
Where aplicable the descriptions should also cover how the proposed measure
contributes to improving quality of life and health and safety (including
working condition), and/or to preserving or enhancing the environment and
natural ressources. This might include the contribution of the proposed work to
meeting relevant regulatory requirements.}

>>>>

\section{European dimension of the problem}
A big part of free or open software development is done in Europe. As an 
example see http://www.debian.org/devel/developers.loc, that gives an overview
of the Debian developers community. There are as more developpers in the 
western part of europe than in the rest of the world.
This community, as others in Europe, uses
hosting platforms in Europe as well as in the rest of the world, mostly of
which are in the United States.
For example, the Savannah hosting architecture is deployed on one machine
located in Boston Massachusset, this machine is vital to the GNU developpers
community and it is replicated using rsync techniques in Europe, although 
the replicating machines have the same informations as the original machine
Europeen developpers are obliged to use the original machine. This situtation
is a threat to the data safety, accessibility and security. Let's imagine that
the building where the computer that is hosting savannah burn, how long 
will it take to set up a new plant usable in the same way that the current
machine is. Nobody knows, even if the data are replicated, the procedures to
switch projects from one machine to another do not exist. Nobody is able to 
guess if it is possible or how long will it take.
Having many hosting facilities divide the global risk brought by a centralized 
approach. Having this hosting facilities in area close to the developpers ones
is a good practice in terms of network usage.
Having hosting facilities designed to support multiligual usage will allow a 
greater number of developpers to start developping using their national 
language, lowering the barrier that prevents them from sharing their code.
\section{European added value of the consortium}
The multinational structure of the consortium will help the consortium being
concerned with multilingual support in the development and contribute to
start the platforms with support for four european languages.
The links between the consortium and the GNU project, many members of the 
consortium are also members of the GNU project,
will foster the dissemination of the project results and help the project
in having a real based installed and used by existing projects.
To ensure the NAME project dissemination it will be packaged so that 
it may be included in existing
distribution non commercial or commercial.
The presence of an industrial partner that will propose services such as
installing, tayloring, and dimensionning hosting platforms for 
industrial purpose, will favour installation of such platforms in industrial
environment to help entreprises in adopting this kind of technologie with a 
reduced access cost. The easy installation features of the product will also
be relevent for industrial usage.
\section{Contribution to EU policies}
The choice of licensing the results of the project under the GNU GPL warrants
that the results will remain available to anyone in the future.
Contributing to adoption of good practice in software development at low
cost, will help improve global software production in europe as well as in
the rest of the world.
Having a hosting platform specific for high education will
contribute to help teaching the best practices for software development in
every university at no extra licensing cost.
Building a network of platforms will help EU in increasing the number of 
developpers that will act for free or open software development. 
The tools used in development platforms may also be used for other kinds of 
groupware activities such as cooperative writing. Providing such tools 
easily instalable and taylorable may help EU to create new networks of 
contributors on different topics such as education (cooperative writing of
courses), helping EU in highering the global level of education by creating
less cost effectives documents.

\chapter*{C4. Contribution to Community social objectives}
\addcontentsline{toc}{chapter}{C4. Contribution to Community social objectives}
\textit{This section, not exceeding two pages, should describe how the proposed
subject wil contribute to meeting the social objectives of the Community, and
should focus on the contribution of the project to improving employment
prospects and the use and development of skills in Europe. \\
Where aplicable the descriptions should also cover how the proposed measure
contributes to improving quality of life and health and safety (including
working condition), and/or to preserving or enhancing the environment and
natural ressources. This might include the contribution of the proposed work to
meeting relevant regulatory requirements.}
\\ \\
The NAME project will help in creating more free/open software in EU by easing 
the access to a software hosting project platform.
\\
The software created using the hosting platforms, resulting from the NAME 
project, will help reduce the software costs for individuals as well as for
small companies and large industrial groups. 
\\
The NAME project will also strengthen existing software by allowing more 
developpers and testers to access hosting platforms and bug reports facilities.
\\
By allowing people to work collectively on projects using their native 
speaking language,
the NAME project will help the documentation translation and generaly the 
software documentation, that will facilitate a larger adoption of free/open
software in the mass of computer users that do not speak english.
\\
